### 2016-12-14 manuscript/manuscript-speed-accuracy.tex
Removed humiliating file conflict info.

We propose that the full spectrum of software tool accuracies and speeds serve a useful purpose to the research community. Like negative results, if honestly reported, illustrate to the research community that certain approaches are not practical research avenues \cite{Ioannidis2005-xh,Workman1999-au,Rivas2000-fb}. The classes of tools that we find in the under-represented accuracy and speed region include some of the most used tools in bioinformatics, such as the homology search tools NCBI-BLAST \cite{Altschul1990-ht,Altschul1997-ga} and HMMER \cite{Eddy:2009} and genome assembly and mapping tools such as AbySS \cite{Simpson:2009}, MAQ \cite{Li:2008} and Newbler \cite{Margulies:2005}. The current practises of publishers, editors, reviewers and authors of software tools therefore deprive our community of tools for building effective and productive workflows.

@@

\textbf{Data extraction and processing:} for each article that met the ALB-criteria and contained data on both the accuracy and speed from their tests we extracted ranks for each method. Many articles contained multiple benchmarks, in these cases we selected a range of these, the provenance of which is stored with the accuracy metric and raw speed and accuracy rank data for each method. In line with rank-based statistics, the cases where methods were tied are resolved by using a midpoint rank (e.g. if method 3 and 4 are tied, the rank 3.5 is used) \cite{Mann1947-re}. Each rank extraction was independently verified by at least one other co-author to ensure both the provenance of the data could be established and that the ranks were correct. The ranks for each benchmark were then normalised to lie between 0 and 1 using the formula $\frac{r-1}{n-1}$ where ‘r’ is a method’s rank and ‘n’ is the number of methods in the benchmark. For methods that were benchmarked multiple times with multiple metrics (e.g. BWA is evaluated in 6 different articles \cite{Bao2011-lv,Caboche2014-lj,Hatem2013-cs,Schbath2012-ob,Ruffalo2011-rl,Holtgrewe2011-fd}) a mean normalised rank is used to summarise the performance.

@@

\section*{Data availability}
The raw datasets are available here:\\
\fussy
\url{https://docs.google.com/spreadsheets/d/14xIY2PHNvxmV9MQLpbzSfFkuy1RlzDHbBOCZLJKcGu8/edit?usp=sharing}\\
\sloppy
Additional documentation, code, figures and raw data is available here:\\
\fussy
\url{https://github.com/UCanCompBio/speed-vs-accuracy-meta-analysis}
\sloppy

@@

>>>>

We propose that the full spectrum of software tool accuracies and speeds serve a useful purpose to the research community. Like negative results, if honestly reported, illustrate to the research community that certain approaches are not practical research avenues \cite{Ioannidis2005-xh,Workman1999-au,Rivas2000-fb}. The classes of tools that we find in the under-represented accuracy and speed region include some of the most used tools in bioinformatics, such as the homology search tools NCBI-BLAST \cite{Altschul1990-ht,Altschul1997-ga} and HMMER2 \cite{Eddy:2009} and genome assembly and mapping tools such as AbySS \cite{Simpson:2009}, MAQ \cite{Li:2008} and Newbler \cite{Margulies:2005}. The current practises of publishers, editors, reviewers and authors of software tools therefore deprive our community of tools for building effective and productive workflows.

@@

\textbf{Data extraction and processing:} for each article that met the ALB-criteria and contained data on both the accuracy and speed from their tests we extracted ranks for each method. Many articles contained multiple benchmarks, in these cases we selected a range of these, the provenance of which is stored with the accuracy metric and raw speed and accuracy rank data for each method. In line with rank-based statistics, the cases where methods were tied are resolved by using a midpoint rank (e.g. if method 3 and 4 are tied, the rank 3.5 is used) \cite{Mann1947-re}. Each rank extraction was independently verified by at least one other co-author to ensure both the provenance of the data could be established and that the ranks were correct. The ranks for each benchmark were then normalised to lie between 0 and 1 using the formula $1-\frac{r-1}{n-1}$ where ‘r’ is a method’s rank and ‘n’ is the number of methods in the benchmark. For methods that were benchmarked multiple times with multiple metrics (e.g. BWA is evaluated in 6 different articles \cite{Bao2011-lv,Caboche2014-lj,Hatem2013-cs,Schbath2012-ob,Ruffalo2011-rl,Holtgrewe2011-fd}) a mean normalised rank is used to summarise the performance.

@@

\section*{Data availability}
Raw datasets, software and documents are available under a CC-BY license:\\
\fussy
\url{https://docs.google.com/spreadsheets/d/14xIY2PHNvxmV9MQLpbzSfFkuy1RlzDHbBOCZLJKcGu8/edit?usp=sharing}\\
and here:\\
\fussy
\url{https://dx.doi.org/10.6084/m9.figshare.4299320.v1}\\
\sloppy
Additional documentation, code, figures and raw data is available here:\\
\fussy
\url{https://github.com/UCanCompBio/speed-vs-accuracy-meta-analysis}
\sloppy

@@

PPG, FAG and NEW are supported by a Rutherford Discovery Fellowship,
administered by the Royal Society of New Zealand. NEW is supported by
a PhD scholarship from the University of Canterbury.
